\begin{minipage}[c]{1.05\textwidth} \centerline{Towards a Continuous Hyperparameter} \centerline{Representation for Neural Networks} \end{minipage}

### 2017-06-26 docs/manuscript/main.tex
Slight change to manuscript.

	  Thus we are led to the question: \emph{Is hyperparameter search a matter of model capacity or model accuracy, and in that distinction, does optimizing hyperparameters with respect to model accuracy coorespond to optimization on model capactiy and visa versa?}  Before we define more specifically model capacity in the context of this question, let us examine this question in two contexts.\

>>>>

	  Thus we are led to the question: \emph{Is hyperparameter search a matter of immediate model accuracy or expected capacity for accuracy, and in that distinction, does optimizing hyperparameters with respect to model accuracy coorespond to optimization on model capactiy and visa versa?}  Let us examine this question in two contexts.\
